---
title: "R Notebook"

```{r}
#install.packages('factoextra')
library(psych)
library(data.table)
library(dplyr)
library(mltools)
library(cluster)
library(factoextra)
library(dplyr)
library(data.table)
library(stats)
library(purrr)
library(cluster)
library(factoextra)
library(gtools)
library(igraph)
library(dplyr)
library(data.table)
library(stats)
library(purrr)
library(cluster)
library(factoextra)
library(gtools)
library(igraph)
```



```{r}
setwd("e:/Downloads/Marketing")
product <- fread('product_table.csv')
transaction <- fread('transaction_table.csv')
transaction <- transaction %>% filter (tran_prod_paid_amt >= 0)
# check missing value
str(transaction)
sapply(transaction,function(x) sum(is.na(x)))
sapply(product,function(x) sum(is.na(x)))
# Joining tables and create new transaction id 
transaction_product <- inner_join(transaction,product, by="prod_id")
transaction_product$new_tran_id <- paste(as.character(transaction_product$tran_dt),as.character(transaction_product$store_id),as.character(transaction_product$cust_id),sep="")
```


Who are the best customers in terms of revenues, profits, transactions/store visits, number of products, etc.?
```{r}
# question 1
transaction_product=as.data.table(transaction_product)
unique(transaction_product[,.(cust_id)]) # 7920 distinct customers
transaction_product[,sum(tran_prod_paid_amt),cust_id][order(V1,decreasing = T)][c(1:792),sum(V1)] # revenues, top 10%
```

DT[, Mean:=mean(X), by=list(Y, Z)]

# revenues, top 10%
transaction_product[,revenue:=sum(tran_prod_paid_amt),by=cust_id][order(revenue,decreasing = T)]
unique(transaction_product[,list(id,revenue)])
# transactions, top 10%
transactioncustomers=transaction_product[,transaction:=length(unique(tran_id)),cust_id][order(transaction,decreasing = T)][c(1:792),] 
# discounts, top 10%
discountcustomers=transaction_product[,discount:=sum(tran_prod_discount_amt)/sum(tran_prod_paid_amt+tran_prod_discount_amt+tran_prod_sale_amt),cust_id][order(discount)][c(1:792),]
# number of products, top 10%
transaction_product[prod_unit=='CT',sum(tran_prod_sale_qty),cust_id][order(V1,decreasing = T)][c(1:792),sum(V1)] # number of products in CT, top 10%
transaction_product[prod_unit=='KG',sum(tran_prod_sale_qty),cust_id][order(V1,decreasing = T)][c(1:792),sum(V1)] # number of products in KG, top 10%
```


```{r}
revenuecustomers
```

















