---
title: "Homework 5"
author: "Carl Xi"
date: "12/05/2019"
output: html_document
---

```{r}
#Initial Setup
options(warn = -1)
#Let's clean the workspace and import the necessary libraries
rm(list = ls(all = TRUE))
library(igraph)
library(Matrix)
library(gdata)
library(proxy)
library(plm)
library(ggplot2)
library(data.table)
library(dplyr)
library(zoo)
library(stringr)
library(hhi)

#let's set the working directory
setwd("C:/Users/carlj/OneDrive/Documents/School-MSBA/Classes/Fall/Social Network Analytics/Assignment 5")

#Import all the datasets
CompanyDetailsRaw <- fread("company_details.csv", header = TRUE)
DealDetailsRaw <- fread("deal_details.csv", header = TRUE)
InvestorDetailsRaw <- fread("investor_details.csv", header = TRUE)
InvestorsDealsRaw <- fread("investors_and_deals.csv", header = TRUE)

#We only care about Venture Capital data from the investors dataset, so let's only keep that
InvestorDetailsRaw <- InvestorDetailsRaw[which(InvestorDetailsRaw$Investor_Type=="Venture Capital"),]

#Let's remove all Deals without a deal date
DealDetailsRaw <- DealDetailsRaw[which(DealDetailsRaw$Deal_Date!=""),]

#transform date into year
DealDetailsRaw$Year <- as.integer(str_sub(DealDetailsRaw$Deal_Date,-2))

#This small function converts the date string which is only 1-2 digits into the full 4-digit format
Yearify <- function(twodigityear){
  #Basically all numbers below 18 (2000-2018) gets added 2000, and everythign else gets added 1900
  if(twodigityear<=18){
    twodigityear = twodigityear+2000
  }
  else{
    twodigityear = twodigityear+1900
  }
  return(twodigityear)
}

#Applying the Yearify Function Above
DealDetailsRaw$Year <- sapply(DealDetailsRaw$Year,Yearify)

#We only need to consider deals that occured after 1990, so let's only keep that
DealDetailsRaw <- DealDetailsRaw[which(DealDetailsRaw$Year>=1990),]

#We will be working with the Primary_Industry_Sector column, so let's remove all NAs there
CompanyDetailsRaw <- CompanyDetailsRaw[!is.na(CompanyDetailsRaw$Primary_Industry_Code),]

#We will be merging the investor and deal datasets later, so let's change the name of the deal column
names(DealDetailsRaw)[1] <- "Deal_Id"

#Let's make sure to only include the deals that we have company information on by checking the company ID
DealDetailsRaw <- DealDetailsRaw[which(DealDetailsRaw$CompanyId %in% CompanyDetailsRaw$CompanyID),]

#We will repeat the three steps above to our investors dataset. Let's only include investors with deals that we have information on by checking the deal IDs
InvestorsDealsRaw <- InvestorsDealsRaw[which(InvestorsDealsRaw$Deal_Id%in%DealDetailsRaw$Deal_Id),]

#Let's adjust the Investor ID column header for easier retrieval later on
names(InvestorDetailsRaw)[1] <- "Investor_Id"

#Let's only keep the investors that we have deal information on
InvestorsDealsRaw <- InvestorsDealsRaw[which(InvestorsDealsRaw$Investor_Id%in%InvestorDetailsRaw$Investor_Id),]


#With data prepared and cleaned, we can now make the CoInvesDealLeadCountComb matrix by merging deal year information with investor/deal data. Let's first make sure that there are no missing rows in the lead_investor column
unique(InvestorsDealsRaw$Lead_Investor)

#Let's create a clean and smaller dataset for our analysis by extracting only the columns we need and merging on deal_id
CleanData1 <- merge(InvestorsDealsRaw[,c(1,2,4)],DealDetailsRaw[,c(1,32)],by="Deal_Id") 
```

```{r}
#With data prepared and cleaned, we can now create the incidence matrix

#Since we only care about co-investments, let's first find the number of investors in each deal
CleanDataSubset1 <- CleanData1 %>% group_by(Deal_Id) %>% summarise(count=length(unique(Investor_Id)))

#Using our number of investors list, we can now subset only the deals with 2 or more investors
CleanDataSubset2 <- CleanDataSubset1[which(CleanDataSubset1$count>1),]

#With criterias ready, we can now subset our data to keep only what we need
CleanDatav2 <- CleanData1[which(CleanData1$Deal_Id%in%CleanDataSubset2$Deal_Id),]

#While we now have only co-investments, not all co-investments have a lead investor. 
CILI <- CleanDatav2 %>% group_by(Deal_Id)%>%  summarise(sum=sum(Lead_Investor))
CILI2 <- CILI[which(CILI$sum>0),]

#We created a list of all the unique years in our data
YearData <- sort(unique(CleanDatav2$Year))
```

```{r}
#We will first construct incidence matrix for co-investments, then transform it to adj matrix by year, and finally turn it into an edge list with weight and year

#Due to how long storing this calculation in a list was taking, we will be using data tables instead for faster matrix multiplication 

#Let's create an empty list to store our following calculations
CombinedEdgeList <- data.table()

#We Run through all the years in our dataset
for(SelectYear in YearData){
  #The first subset is all entries in our clean dataset of the select year
  Subset1 <- CleanDatav2[which(CleanDatav2$Year==SelectYear),]
  #From the first subset, we cast another matrix with investor ID on X and Deal ID on Y
  Subset2 <- as.matrix(data.frame(dcast(Subset1[,c(1,2)], Investor_Id ~ Deal_Id, fun.aggregate=length), row.names = 1),sparse = TRUE)
  
  #We then take the cross product of the transpose of the two sets that we have created above
  CombSubset <- tcrossprod(Subset2,Subset2)
  
  diag(CombSubset) <- 0
  CombGraph<- graph.adjacency(CombSubset,weighted=TRUE,mode = "undirected")
  GraphDataFrame <- get.data.frame(CombGraph)
  GraphDataFrame$year <- SelectYear
  CombinedEdgeList <- rbind(CombinedEdgeList,GraphDataFrame)
}

#We have to loop through all the years again, but this time we look at the number of co-investment leads in the recent 5 years
CoInvestCount <- data.table()
for(SelectYear in YearData){
  Subset1 <- CombinedEdgeList[which((CombinedEdgeList$year<=SelectYear)&(CombinedEdgeList$year>SelectYear-5)),] %>% group_by(from,to) %>% summarise(year=SelectYear,count=sum(weight))
  CoInvestCount <- rbind(CoInvestCount,as.data.frame(Subset1))
}

#We output our results to a CSV file for further processing.
write.csv(CoInvestCount,"CoInvestCount.csv")

#Let's now create the Lead Investor Edge List
DealLeadEdgeList <- data.table()

#We only want deals that are also in our co-investor Lead-Investor subset
CoInvesLeadInvestSet <- CleanDatav2[which(CleanDatav2$Deal_Id%in%CILI2$Deal_Id),]
CoInvesLeadInvestClean <- unique(CoInvesLeadInvestSet$Deal_Id)

#We loop through each deal in the clean Co-Investment Lead-Investment dataset, selecting each deal and encoding them into the empty DealLeadEdgeList we created above
for(SelectDeal in CoInvesLeadInvestClean){
  Subset1 <- CoInvesLeadInvestSet[which(CoInvesLeadInvestSet$Deal_Id==SelectDeal),]
  Subset2 <- expand.grid(unlist(Subset1[which(Subset1$Lead_Investor==1),2]),unlist(Subset1[,2]))
  Subset2$year <- Subset1$Year
  DealLeadEdgeList <- rbind(DealLeadEdgeList,Subset2)
}

#We make sure to set the column names right then export the data into a CSV
colnames(DealLeadEdgeList) <- c("lead","non","year")
write.csv(DealLeadEdgeList,"DealLeadEdgeList.csv")

#Again, we repeat the same process as above and only look at the number of co-investment leads in the recent 5 years
DealLeadCount <- data.table()
for(SelectYear in YearData){
  Subset1 <- DealLeadEdgeList[which((DealLeadEdgeList$year<=SelectYear)&(DealLeadEdgeList$year>SelectYear-5)),] %>% group_by(lead,non) %>% summarise(year=SelectYear,count=n())
  DealLeadCount <- rbind(DealLeadCount,as.data.frame(Subset1))
}

#We make sure our DealLeadCount set is in the right format then export it to a CSV for further processing as above
DealLeadCount$lead <- as.character(DealLeadCount$lead)
DealLeadCount$non <- as.character(DealLeadCount$non)
DealLeadCount <- DealLeadCount[which(DealLeadCount$lead!=DealLeadCount$non),]
write.csv(DealLeadCount,"DealLeadCount.csv")

#We will reconstruct the CoInvestCount but exclude all entries with the same from and to investor ID
CoInvestCount <- CoInvestCount[which(CoInvestCount$from!=CoInvestCount$to),]
CoInvestCountSubset <- cbind(CoInvestCount[,2],CoInvestCount[,1],CoInvestCount[,c(3,4)])
colnames(CoInvestCountSubset) <- c("from","to","year","count")
CoInvestCount <- rbind(CoInvestCount,CoInvestCountSubset)
colnames(CoInvestCount) <- c("lead","non","year","countshare")
colnames(DealLeadCount) <- c("lead","non","year","leadshare")

#We can now merge the Co-Invest Count and Deal Lead Count information by lead, non, and year columns
CoInvesDealLeadCountComb <- merge(CoInvestCount,DealLeadCount,by=c("lead","non","year"),all.x = TRUE)
CoInvesDealLeadCountComb[which(is.na(CoInvesDealLeadCountComb$leadshare)),5] <- 0
CoInvesDealLeadCountComb$value <- CoInvesDealLeadCountComb$leadshare/CoInvesDealLeadCountComb$countshare

#We can take a subset of only the columns we need
CIDLCountCombSubset <- CoInvesDealLeadCountComb[,c(1,2,3,5)]
colnames(CIDLCountCombSubset)[4]<-"weight"

#We create an empty datatable to store our calculations
CombinedEigenGraph <- data.table()
#Like above, we loop through every year, take a subset of the columns we need for each year, make a graph, calculate the 
for(SelectYear in YearData){
  Subset1 <- CIDLCountCombSubset[which(CIDLCountCombSubset$year==SelectYear),c(1,2,4)]
  Subset2 <- graph.data.frame(Subset1,directed=TRUE)
  EigenCent <- eigen_centrality(Subset2, directed = TRUE, weights = NULL)$vector
  CombGraph <- as.data.table(cbind(names(EigenCent),unname(EigenCent)))
  CombGraph$year <- SelectYear
  CombinedEigenGraph <- rbind(CombinedEigenGraph,CombGraph)
}

write.csv(CombinedEigenGraph,"CombinedEigenGraph.csv")

```

1. a) Traditionally, venture capital analysis have only considered the concentration of a venture capital firms investments in to different portfolio categories. The more concentrated a firm’s investments, the less diversified it is. 

```{r}
#Let's first calculate the Herfindahl Index

#Let's find all the unique Industries
IndustryList <- unique(CompanyDetailsRaw$Primary_Industry_Code)

#We go back to the raw data and merge company ID to our deals by the deal ID column
CleanDataQ1 <- merge(CleanData1,DealDetailsRaw[,c(1,2)],by="Deal_Id",all.x = TRUE)

#We standardize the company ID column header
colnames(CleanDataQ1)[5]<-"CompanyID"

#We then go back again and extract the primary industry code information and add it to our data
CleanDataQ1 <- merge(CleanDataQ1,CompanyDetailsRaw[,c(1,8)],by="CompanyID",all.x = TRUE)

#We group our new dataset with the two columns added by investor id, year, and finally industry code, and conduct the necessary mutation
CleanDataQ1v2 <- CleanDataQ1 %>% group_by(Investor_Id,Year,Primary_Industry_Code) %>% summarise(count=n())%>% group_by(Investor_Id,Year) %>% mutate(Percentage=count/sum(count)*100)

#We take a subset of only unique investors every year
DataQ1Subset <- unique(CleanDataQ1v2[,c(1,2)])

#We Create an empty list for the percentages
DataQ1Subset$Percent <- NA

#We then loop through each investor and calculate their index percentages
for(i in (1:dim(DataQ1Subset)[1])){
  Subset1 <- CleanDataQ1v2[(which((CleanDataQ1v2$Investor_Id==DataQ1Subset[i,]$Investor_Id)&(CleanDataQ1v2$Year==DataQ1Subset[i,]$Year))),c(3,5)]
  Subset2 <- hhi(as.data.frame(Subset1),"Percentage")
  #We encode the calculated value into the Percent column
  DataQ1Subset[i,3] <- Subset2
}

#Again, we export the results for further analysis
write.csv(DataQ1Subset,"DataQ1Subset.csv")
```


```{r}
#This time, we are merging our subset with the index values with our eigen graph from above. We first need to make sure the column names match up
colnames(CombinedEigenGraph) <- c("Investor_Id","score","Year")
EigenGraphCompany <- merge(CombinedEigenGraph,DataQ1Subset,by=c("Investor_Id","Year"),all.x = TRUE)
#After the merge, we remove all NA columns
EigenGraphCompany <- na.omit(EigenGraphCompany)

#We then group our data by investor ID and calculate the lag score
EigenGraphCompanyv2 <- EigenGraphCompany %>% group_by(Investor_Id) %>% mutate(lag.score = dplyr::lag(score, n = 1, default = NA))

#Again, we make sure to remove all NAs
EigenGraphCompanyv2 <- na.omit(EigenGraphCompanyv2)
```
Run a regression predicting a venture capital firm’s concentration in a year based on its status in the prior year it made an investment and also include the square of this term. One motivation that might influence venture capital investors to diversify might be to minimize risk. In order to isolate the effect of status from this alternative rationale, include lagged control variables for a venture capital firm’s risk exposure:

• whether a venture capital firm tends to originate its own deals: for more than 50% of the companies it invests in, it invests in the first investment round this company has received

• whether a venture capital firm tends to invest in the IT sector: more than 50% of the companies it invests in are in the company-level variable Primary Industry Sector “Information Technology”

• whether a venture capital firm tends to invest in early-stage startups: more than 50% of the companies it invests in are of the Deal Type 1 “Early Stage VC”, “Accelerator/Incubator”, “Seed Round”, or “Angel (individual)”

```{r}
#To see if the second point is true (more than 50% investments in the IT sector), we need to find the Industry of each deal in our Clean Dataset for Q1 
CleanDataQ1 <- merge(CleanDataQ1,CompanyDetailsRaw[,c(1,6)],by="CompanyID",all.x = TRUE)

#Then we group by investor, year and finally industry to calculate the percentage, this is similar to above the index calculation process above
ITCalc <- CleanDataQ1 %>% group_by(Investor_Id,Year,Primary_Industry_Sector) %>% summarise(count=n())%>% group_by(Investor_Id,Year) %>% mutate(Percentage=count/sum(count)*100)

#We are finally ready to run our first model, we first run 

#Model1<-plm(Percent ~ lag.score + I(lag.score*lag.score), data = EigenGraphCompanyv2, model = "within", effect="individual",random.method="amemiya")

#This was suppuosed to work but I ran into the following problem:
#Error in plm.fit(data, model, effect, random.method, random.models, random.dfcor, : 0 (non-NA) cases"
#Did not have time to debug

#I will re-submit my assignment with more questions completed hopefully soon.
```

